Figures

### 2023-03-21 figures/figures.Rmd
look at more distant sites

dt_sites$dist <- unlist(list(unlist(st_distance(coords_ire, dt_sites)))) / 1609.34
dt_sites_close <- dt_sites[dt_sites$dist < 100,]
head(dplyr::arrange(dt_sites_close, dist)$dist)

>>>>

dt_sites$dist <- unlist(list(unlist(st_distance(coords_ire, dt_sites)))) / 1609.34
dt_sites_close <- dt_sites[dt_sites$dist < 100,] %>%
    dplyr::arrange(dist)
head(dt_sites_close$dist)
st_coordinates(dt_sites_close[1,])
